MATH/COMP 562 ASSIGNMENT 2

### 2023-06-29 assignment-2/article.tex
Fix whitespace
Finish adding problems for Convex Learning Problems section

\subsection*{Exercise 1.4 (non convexity of 0\-1 loss)}
Problem 12.1. Hint: Consider samples in a checkerboard pattern.

\subsection*{Exercise 1.5 (Convexity, Lipschitz, and Smoothness of logistic regression loss)}
Problem 12.2.

\subsection*{Exercise 1.6 (Lipschitz continuity of the hinge loss)}
Problem 12.3.

>>>>

\begin{problem}{Exercise 1.4 (non convexity of 0\textendash{}1 loss)}
Construct an example showing that the 0\textendash{}1 loss function may suffer from local minima; namely, construct a training sample $S \in {(X \times \{\pm1\})}^m$ (say, for $X = \mathbb{R}^2$), for which there exist a vector $w$ and some $\varepsilon > 0$ such that:
\begin{enumerate}

	\item For any $w'$ such that $\|w - w'\| \leq \varepsilon$ we have $L_S (w) \leq L_S (w')$ (where the loss here is the 0\textendash{}1 loss). This means that $w$ is a local minimum of $L_S$.
	\item There exists some $w^*$ such that $L_S (w^*) < L_S (w)$. This means that $w$ is not a global minimum of $L_S$.
\end{enumerate}

Hint: Consider samples in a checkerboard pattern.
\end{problem}

\begin{solution}

\end{solution}

\begin{problem}{Exercise 1.5 (Convexity, Lipschitz, and Smoothness of logistic regression loss)}
Consider the learning problem of logistic regression: Let $H = X = \{x \in \mathbb{R}^d : \|x\| \leq B\}$, for some scalar $B > 0$, let $Y = \{\pm1\}$, and let the loss function $\ell$ be defined as $\ell(w, (x, y)) = \log(1 + \exp(-y\langle w, x \rangle))$. Show that the resulting learning problem is both convex-Lipschitz-bounded and convex-smooth-bounded. Specify the parameters of Lipschitzness and smoothness.
\end{problem}

\begin{solution}

\end{solution}

\begin{problem}{Exercise 1.6 (Lipschitz continuity of the hinge loss)}
Consider the problem of learning halfspaces with the hinge loss. We limit our domain to the Euclidean ball with radius $R$. That is, $X = \{x : \|x\|_2 \leq R\}$. The label set is $Y = \{\pm1\}$ and the loss function $\ell$ is defined by $\ell(w, (x, y)) = \max\{0, 1 - y\langle w, x \rangle\}$. We already know that the loss function is convex. Show that it is $R$-Lipschitz.
\end{problem}

\begin{solution}

\end{solution}
